\documentclass{article}
\title{Matrix Basic Fixture}
\author{Harness}
\date{2026}
\begin{document}
\maketitle

\begin{abstract}
Abstract prose sits in a small environment and is edited by the abstract scenario here.
\end{abstract}

\section{Alpha}
\label{sec:alpha}

Short prose paragraph for the exact tier baseline.

A much longer prose paragraph follows so the line breaker has real work to do, with
enough words that the paragraph wraps across at least three visual lines in the
column, giving the locate ladder several baselines to verify against while the
matrix types a character into the middle of it.

\paragraph{Runin} Prose following a run-in heading continues on the very same line
and wraps onward with additional words so the heading merge scenario has body text.

\subsection{Beta}

Paragraph referencing Section~\ref{sec:alpha} so reference resolution is exercised.

\begin{itemize}
\item First bullet item text goes here.
\item Middle bullet item text goes here.
\item Last bullet item text goes here.
\end{itemize}

\begin{enumerate}
\item First numbered item text.
\item Middle numbered item text.
\item Last numbered item text.
\end{enumerate}

\begin{equation}
E = m c^2 + \int_a^b \frac{a}{b} \, dx
\end{equation}

\begin{tabular}{ll}
alpha & one \\
beta & two \\
\end{tabular}

Paragraph carrying a footnote\footnote{Footnote body text for the footnote scenario.}
in the middle of it plus enough extra words to wrap onto a second line cleanly.

Closing paragraph after everything else in the document body ends the fixture.

\end{document}
